---
title: "Volume v Depth Experiments"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Volume vs Depth

Making some imaginary data to test whether volume and depth should have the same agreement. 
The SD-6 WRG analysis suggests that volume agrees better than depth.
Question is: if we are dividing by the same area, should this be possible?

## Make some imaginary data

Will make data where depth is not correlated (random numbers), area is perfectly correlated, and volume is depth*area.

```{r make-data}

set.seed(1)
pretendDepth_sim <- runif(500)
pretendDepth_obs <- runif(500)
pretendArea_sim <- seq(1, 500)
pretendArea_obs <- seq(1, 500)
pretendVolume_sim <- pretendDepth_sim*pretendArea_sim
pretendVolume_obs <- pretendDepth_obs*pretendArea_obs

```

## Compare pretend irrigation depth

Depth not correlated - random numbers.

```{r compare-depth}

plot(pretendDepth_sim, pretendDepth_obs)

summary(lm(pretendDepth_obs ~ pretendDepth_sim))

```
## Compare pretend irrigated area

Area perfectly correlated - defined equal to each other.

```{r compare-area}

plot(pretendArea_sim, pretendArea_obs)

summary(lm(pretendArea_obs ~ pretendArea_sim))

```

## Compare pretend irrigation volume

Multiplying depth * area.

```{r compare-volume}

plot(pretendVolume_sim, pretendVolume_obs)

summary(lm(pretendVolume_obs ~ pretendVolume_sim))

```